% Set a sane document class, 12pt font, and a report template
\documentclass[a4paper, twoside, openright, 12pt]{report}

% Import used packages
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{parskip}
\usepackage{color}
\usepackage{multirow}
%\usepackage[lmargin=25mm,rmargin=25mm,tmargin=40mm,bmargin=30mm]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage[x11names, rgb]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{decorations,arrows,shapes}
\usepackage{amsmath}



% Bibliographies
\usepackage[defernumbers=true]{biblatex}
\bibliography{bibliography}

% Use UTF-8
%\usepackage[utf8x]{inputenc}
\def \authors {Ken B\o{}rge Melhus Viktil \& Martin Tobias Holmedahl Sandsmark}
\def \papertitle {Jantu - A Cognitive Agent Playing StarCraft: Brood War}

% Meta-information for the PDF
\hypersetup{
pdfauthor = \authors,
pdftitle = \papertitle,
pdfsubject = {Master project for IDI},
pdfkeywords = {project, cognitive, architecture, starcraft, artificial
    intelligence},
pdfcreator = {LaTeX with hyperref package lol},
pdfproducer = {pdflatex}}

%opening
\title{\papertitle}
\author{\authors}

\begin{document}

% Abstract in english
\begin{abstract}
It has been shown that most players enjoys playing video games against other human players instead of computer controlled opponents. But most research on artificial intelligence in gaming today focus on just winning in the most effective way possible, instead of making the agents more human-like.

Cognitive architectures are designed to emulate how the human brain operates when performing tasks. Very little research has been done on applying cognitive methods to the field of real-time strategy games.

In this paper we aim to research the use of a cognitive model that is capable of playing StarCraft: Brood War with decent results. The result is an AI agent implemented with a cognitive framework called LIDA. The resulting agent is only a proof of concept implementation, but we provide suggestions for how it can be improved in the future, and where the problems and limitations of our approach lies.
\end{abstract}
\thispagestyle{empty}
\cleardoublepage

% Abstract in norwegian
\renewcommand{\abstractname}{Sammendrag}
\begin{abstract}
Det har vist seg at folk som spiller spill foretrekker å spille mot andre mennesker, i motsetning til å spille mot kunstige spillere, men størstedelen av forskningen på kunstig intelligens i spill i dag fokuserer mer på å vinne mest mulig effektivt, istedenfor å se på hvordan man kan få de til å spille mer menneskelig.

Kognitive arkitekturer er laget for å emulere hvordan den menneskelige hjernen utfører oppgaver. Det er per dags dato nesten ikke noe forskning på bruk av kognitive arkitekturer innen sanntidsstrategispill.

I denne teksten vil vi undersøke bruken av en kognitiv modell for å spille StarCraft: Brood War. Resultatet er en agent implementert med programvarerammeverket LIDA. Agenten er en prototypeimplementasjon, men vi kommer også med forslag til hvordan den kan forbedres i fremtiden, og hvilke problemer og begrensninger tilnærmingen vår har.
\end{abstract}
\thispagestyle{empty}
\cleardoublepage

% Acknowledgements
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
Firstly we would like to thank our supervisors; Helge Langseth and Anders Kofod-Petersen. We would also like to thank the Cognitive Computing Research Group at the University of Memphis, for their LIDA framework which is the basis of our project. Finally we would like to thank the developers of the BWAPI project, and in particular Adam Heinermann, as well as the rest of the members in the \#BWAPI IRC channel on Freenode.
\end{abstract}
\thispagestyle{empty}
\cleardoublepage

\pagenumbering{roman}

% TOC
\tableofcontents
\cleardoublepage

% Figures
\listoffigures
\cleardoublepage

% Tables
\listoftables
\cleardoublepage


% Content
\pagestyle{fancy}
\pagenumbering{arabic}

\include{introduction}
\include{theory}
\include{implementation}
\include{results}
\include{evaluation}
\endrefsection

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography

\end{document}
